---
title: "Provide MeSHDb databases for AnnotationHub"
author: "Koki Tsuyuzaki"
graphics: no
package: AHMeSHDbs
output:
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Provide MeSHDb databases for AnnotationHub}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
    %\VignetteDepends{AnnotationHub}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Authors**: `r packageDescription("AHMeSHDbs")[["Author"]] `<br />
**Last modified:** `r file.info("creating-MeSHDbs.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Fetch `MeSHDb` databases from `AnnotationHub`

The `AHMeSHDbs` package provides the metadata for all `MeSHDb` SQLite databases
in `r Biocpkg("AnnotationHub")`.
First we load/update the `AnnotationHub` resource.

```{r load-lib, message = FALSE}
library(AnnotationHub)
ah <- AnnotationHub()
```

Next we list all `MeSHDb` entries from `AnnotationHub`.

```{r list-MeSHDb}
query(ah, "MeSHDb")
```

We can confirm the metadata in AnnotationHub in Bioconductor S3 bucket
with `mcols()`.

```{r confirm-metadata}
mcols(query(ah, "MeSHDb"))
```

We can query only the MeSHDb SQLite files for species *Mus musculus*.

```{r query-mouse}
qr <- query(ah, c("MeSHDb", "Mus musculus"))
# filepath_mmu <- qr[[1]]
```

This filepath is can be specified with the argument of `RSQLite::dbConnect` and
`MeSHDbi::MeSHDb` and also used as the argument of `meshr`, which is an
R/Bioconductor package for MeSH enrichment analysis.

For the details, check the vignettes of `RSQLite`, `MeSHDbi`, and `meshr`.

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```